R for Clinical Study Reports and Submission

### 2022-03-24 index.Rmd

>>>>

## Events {-}

```{css, echo=FALSE}
table { font-variant-numeric: tabular-nums; }
table.table td:nth-child(1) { min-width: 28ch; }
table.table td:nth-child(2) { min-width: 14ch; }
table.table td:nth-child(3) { min-width: 14ch; }
table.table tbody { border-bottom: 1px solid #B6BDC6; }
```

```{r, echo=FALSE}
knitr::kable(read.table("events.tsv", stringsAsFactors = FALSE, header = TRUE, sep = "\t"))
```
